---
title: "Code for Graphs for ASN presentation"
output: html_notebook
---
This document contains the code for the graphs I'll include in my 2021 ASN presentation, as well as model results I'll present. 

As such, it doesn't contain all models or all graphs - see WorkingScript.Rmd for a stream-of-consciousness view of my work.

## Load in packages

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(lubridate)
library(viridisLite)
```

## Load in data

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

## Manipulate data into correct forms

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
data <- data[complete.cases(data[, 1]), ]

data$outcome <- data$fate

data$outcome <- gsub(" mongo", "", data$outcome)
data$outcome <- gsub("em", "we", data$outcome)

data$mass.max <- data$mass.max / 1000 

```


```{r}
#1
scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)

#0
unique <- unique(scan$comb)
consumed <- as.data.frame(unique)
consumed$area <- 0

#2-4
for (i in 1:length(consumed$unique)){
    subset <- filter(scan, scan$comb == consumed[i, 1])
    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
    consumed[i, 2] <- value
}  

#5
consumed <- consumed %>%
  separate(unique, c("catID", "leafID"), "_")

#6
ID <- unique(consumed$catID)
consumedsum <- as.data.frame(ID)
consumedsum$totalarea <- 0

#7
for (i in 1:length(consumedsum$ID)){
  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
  value2 <- sum(subset2$area)
  consumedsum[i, 2] <- value2
}

#8
consumedsum$ID <- as.numeric(consumedsum$ID)

consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]

data <- data[data$ID %in% consumedsum$ID, ]

consumedsum <- consumedsum[order(consumedsum$ID), ]

data$area <- consumedsum$totalarea

```

```{r}
# Internal process of the loop to convert days to dates
expt_day <- function(start.date, date){
  date <- mdy(date)
  start <- mdy(start.date)
  diff <- yday(date) - yday(start)

  return(diff)
}

# Code for the loop itself
loop <- function(start.date, date.list){
  days <- rep(NA, length(date.list))
  for (i in 1:(length(days))){
    days[i] <- expt_day(start.date = start.date, date = date.list[i])
  }
  return(days)
}
```

```{r}
data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)

data$ttmax <- data$day.max - data$day.hatch
```

```{r}
data$perc.w.ecl <- data$num.w.eclos / (data$num.w.coc + data$num.w.larvae)
data$num.w.total <- (data$num.w.coc + data$num.w.larvae)

data$HS <- factor(data$HS, levels = c("yes", "no"))
data$para <- factor(data$para, levels = c("yes", "no"))
```


## Graphs

### Maximum mass gained and age at that point

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), 
       data = data[data$para == "no", ]) +
  theme_bw() + 
  ylim(0, 20) + 
  xlim(15, 45) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 17, 2)) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN1.png", width = 8, height = 5)
```

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), 
       data = data[data$treatment != "P HS", ]) +
  theme_bw() + 
  ylim(0, 20) + 
  xlim(15, 45) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 2)) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN2.png", width = 8, height = 5)
```

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = food, shape = treatment), data = data) +
  theme_bw() + 
  ylim(0, 20) + 
  xlim(15, 45) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 17, 2)) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (g)", 
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN3.png", width = 8, height = 5)
```

### Maximum mass compared to plant matter consumed


```{r}
ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
       data = data[data$para == "no", ]) + 
  theme_bw() + 
  xlim(0, 6000) + 
  ylim(0, 20) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 17, 2)) + 
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (g)",
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN4.png", width = 8, height = 5)
```


```{r}
ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), 
       data = data[data$treatment != "P HS", ]) + 
  theme_bw() + 
  xlim(0, 6000) + 
  ylim(0, 20) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 2)) + 
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (g)",
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN5.png", width = 8, height = 5)
```


```{r}
ggplot(aes(x = area, y = mass.max, color = food, shape = treatment), data = data) + 
  theme_bw() + 
  xlim(0, 6000) + 
  ylim(0, 20) + 
  geom_point() + 
  scale_shape_manual(values = c(19, 1, 17, 2)) + 
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (g)",
       shape = "Treatment", color = "Hostplant Consumed")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN6.png", width = 8, height = 5)
```



### Wasp fate

```{r}
ggplot(aes(x = num.w.total, y = perc.w.ecl, color = food), data = data) + 
  theme_bw() + 
  ylim(0, 1.05) + 
  geom_point(aes(shape = treatment)) + 
  scale_shape_manual(values = c(19, 1, 17, 2)) +
  labs(x = "Number of wasp larvae emerged", y = "Proportion of wasps eclosed", color = "Hostplant Consumed", 
       shape = "Heat Shock Status")

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/ASN7.png", width = 8, height = 5)
```

# ----- ARCHIVE ----- DO NOT RUN -----

## Graphs

```{r}
TBdata <- data[data$food == "TB", ]
DCdata <- data[data$food == "DC", ]
```

Three colors I'm using: 

("#66CB5D", "#21908D", "#3E4F8A", "#450D54")
("#460F5A", "#87D548", "#30B67B")


wander: #882255
we: #88CCEE
wowe: #117733

### Wasp fate

```{r}
ggplot(aes(x = num.w.total, y = perc.w.ecl, color = HS), data = data) + 
  theme_bw() + 
  ylim(0, 1.05) + 
  geom_smooth(method = "lm", se = F) +
  geom_point(alpha = 0.8, aes(shape = food)) + 
  scale_shape_manual(values = c(19, 6)) +
  scale_color_manual(values = c("#EF000D", "#00CFD2")) + 
  labs(x = "Number emerged", y = "Percentage of wasps eclosed", shape = "Hostplant Consumed", 
       color = "Heat Shock Status")
```


### Maximum mass gained and age at that point

```{r}
ggplot(aes(x = ttmax, y = mass.max, color = outcome, shape = food), data = data) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_shape_manual(values = c(19, 6)) + 
  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
       color = "Developmental Outcome", shape = "Hostplant Consumed")
```

```{r}
dataPHS <- data[data$treatment == "P HS", ]

ggplot(aes(x = ttmax, y = mass.max, color = fate), data = dataPHS) +
  theme_bw() + 
  geom_point(alpha = 0.8) + 
  scale_color_manual(values = c("#66CB5D", "#21908D", "#3E4F8A", "#450D54")) + 
  labs(x = "Development time at maximum mass (days)", y = "Maximum mass achieved (mg)", 
       color = "Developmental Outcome")
```


### Maximum mass compared to plant matter consumed

```{r}
ggplot(aes(x = area, y = mass.max), data = data) + 
  theme_bw() + 
  geom_point(aes(color = outcome, shape = food)) + 
  scale_shape_manual(values = c(19, 6)) + 
  scale_color_manual(values = c("#882255", "#88CCEE", "#117733")) +
  labs(x = "Leaf surface area consumed (cm2)", y = "Maximum mass achieved (mg)",
       color = "Developmental Outcome", shape = "Hostplant Consumed")
```


