---
title: "Working Script"
output: html_notebook
---

This script is just to play around with the data while I'm still collecting it. 

## Load in packages

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lme4)
library(lubridate)
```


## Load in the data

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedNov30modfinal.csv")
```


## Counting sample size

```{r}
count(data[data$food == "TB" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "no", ])
```

```{r}
count(data[data$food == "DC" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "no", ])
```

## Check how many have survived

```{r}
data <- data[data$fate != "dead" & data$fate != "quink", ]
```

```{r}
count(data[data$food == "TB" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "TB" & data$para == "no" & data$HS == "no", ])
```

```{r}
count(data[data$food == "DC" & data$para == "yes" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "yes" & data$HS == "no", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "yes", ])
count(data[data$food == "DC" & data$para == "no" & data$HS == "no", ])
```

## Load in the leaf area data

```{r}
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

## Write a for-loop for getting the amounts eaten 

0. Create output file 
1. Combine Leaf ID and cat ID into one ID 
2. Parse by unique  ID
3. Subtract min measurement from max measurement
4. Record with comb ID
5. Separate out catID and leaf ID
6. Create new output structure
7. Sum for each cat ID 
8. Combine with main dataset as a column

```{r}
#1
scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)

#0
unique <- unique(scan$comb)
consumed <- as.data.frame(unique)
consumed$area <- 0

#2-4
for (i in 1:length(consumed$unique)){
    subset <- filter(scan, scan$comb == consumed[i, 1])
    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
    consumed[i, 2] <- value
}  

#5
consumed <- consumed %>%
  separate(unique, c("catID", "leafID"), "_")

#6
ID <- unique(consumed$catID)
consumedsum <- as.data.frame(ID)
consumedsum$totalarea <- 0

#7
for (i in 1:length(consumedsum$ID)){
  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
  value2 <- sum(subset2$area)
  consumedsum[i, 2] <- value2
}

```

Step 8 proved to be more complicated, so it's listed below... 

```{r}
consumedsum$ID <- as.numeric(consumedsum$ID)

consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]

data <- data[data$ID %in% consumedsum$ID, ]

consumedsum <- consumedsum[order(consumedsum$ID), ]

data$area <- consumedsum$totalarea
```

YAY!!!

# Graphing

Let's graph maximum mass reached:

```{r}
ggplot(data = data, aes(x = mass.max)) + 
  geom_histogram(binwidth = 500)
```

Now, let's graph area to see if it's "normal". 

```{r}
ggplot(data, aes(x = area)) + 
  geom_histogram(binwidth = 250)
```
Nope, definitely bimodal

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  theme_bw() + 
  geom_point(aes(color = food)) + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Food type")
```

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  theme_bw() + 
  geom_point(aes(color = fate, shape = food)) + 
  #scale_color_viridis_d() + 
  scale_shape_manual(values = c(19,6)) + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)")
```
```{r}
data <- data[data$fate != "wander*", ]

modfate <- lmer(mass.max ~ fate*food + (1|bin), data = data)

summary(modfate)
```


```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  theme_bw() + 
  geom_point(aes(color = treatment)) + 
  scale_color_viridis_d() + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Treatment")
```

Now, let's run some preliminary analyses (this is probably whack because it's bimodal):

```{r}
mod1 <- lm(area ~ food*para*HS + mass.max, data = data)

summary(mod1)
```

```{r}
mod1.5 <- lm(area ~ mass.max + food, data = data)

summary(mod1.5)
```

```{r}
mod1.75 <- lm(area ~ mass.max + food*para, data = data)

summary(mod1.75)
```

```{r}
mod1.9 <- lm(area ~ food*para*HS, data = data)

summary(mod1.9)
```


```{r}
mod2 <- lm(mass.max ~ food*para*HS, data = data)

summary(mod2)
```

```{r}
mod3 <- lm(area ~ mass.max, data = data)

summary(mod3)
```

```{r}
mod3.5 <- lm(mass.max ~ area, data = data )

summary(mod3.5)
```

```{r}
dataDC <- data[data$food == "DC", ]
dataTB <- data[data$food == "TB", ]

t.test(dataDC$area, dataTB$area)
```

## Adding in random effect of bin 

```{r}
mod4 <- lmer(area ~ mass.max + (1|bin), data = data)

summary(mod4)
```

It's a singluar fit - I could switch all of my individual bins to the same number? Would that work? 

Let's check the effect of group vs. individual bins

```{r}
mod5 <- lmer(area ~ mass.max + (1|bin.type), data = data)

summary(mod5)
```

```{r}
mod6 <- lmer(mass.max ~ food*para*HS + (1|bin), data = data)

summary(mod6)
```

```{r}
mod6.5 <- lmer(mass.max ~ food + para + HS + (1|bin), data = data)

summary(mod6.5)
```


The above model is the only one that isn't singular!! 

```{r}
mod7 <- lmer(mass.max ~ food*para*HS + (1|bin.type), data = data)

summary(mod7)
```

```{r}
mod8 <- lmer(mass.max ~ para*HS + (1|bin), data = data)

summary(mod8)
```


Let's test some models with AIC

```{r}
AIC(mod1, mod1.5, mod1.75, mod3, mod4, mod5)
```

Model 1 and model 1.75 are indistinguishable - so you need food and para and their interaction to get the full picture for area

```{r}
AIC(mod2,mod6, mod6.5, mod7, mod8)
```

Mods 6 and 7 are indistinguishable - you need the random effect of bin, but bin and bin type have the same effect? You also need all the interactive terms, even though they aren't significant. 

```{r}
data2 <- read.csv("~/Desktop/MsCcHSFeedSep15binmod2.csv")
```

```{r}
consumedsum2 <- consumedsum[consumedsum$ID %in% data2$ID, ]

data2 <- data2[data2$ID %in% consumedsum2$ID, ]

consumedsum2 <- consumedsum2[order(consumedsum2$ID), ]

data2$area <- consumedsum2$totalarea
```

Let's try it now 

```{r}
modcomb <- lmer(area ~ mass.max + (1|bin), data = data2)

summary(modcomb)
```

## Age vs. Mass plots 

```{r}
# Internal process of the loop to convert days to dates
expt_day <- function(start.date, date){
  date <- mdy(date)
  start <- mdy(start.date)
  diff <- yday(date) - yday(start)

  return(diff)
}

# Code for the loop itself
loop <- function(start.date, date.list){
  days <- rep(NA, length(date.list))
  for (i in 1:(length(days))){
    days[i] <- expt_day(start.date = start.date, date = date.list[i])
  }
  return(days)
}

# Convert all the dates to days

data$day.hatch <- loop(start.date = "07/12/2020", date.list = data$date.hatch)
data$day.3rd <- loop(start.date = "07/12/2020", date.list = data$date.3rd)
data$day.4th <- loop(start.date = "07/12/2020", date.list = data$date.4th)
data$day.5th <- loop(start.date = "07/12/2020", date.list = data$date.5th)
data$day.w <- loop(start.date = "07/12/2020", date.list = data$date.w)
data$day.remove <- loop(start.date = "07/12/2020", date.list = data$date.remove)
#data$day.5th.2 <- loop(start.date = "07/12/2020", date.list = data$date.5th.2)
#data$day.5th.3 <- loop(start.date = "07/12/2020", date.list = data$date.5th.3)
#data$day.5th.4 <- loop(start.date = "07/12/2020", date.list = data$date.5th.4)
#data$day.6th <- loop(start.date = "07/12/2020", date.list = data$date.6th)
#data$day.6th.2 <- loop(start.date = "07/12/2020", date.list = data$date.6th.2)
#data$day.6th.3 <- loop(start.date = "07/12/2020", date.list = data$date.6th.3)
#data$day.7th <- loop(start.date = "07/12/2020", date.list = data$date.7th)
#data$day.7th.2 <- loop(start.date = "07/12/2020", date.list = data$date.7th.2)
#data$day.7th.3 <- loop(start.date = "07/12/2020", date.list = data$date.7th.3)
data$day.max <- loop(start.date = "07/12/2020", date.list = data$date.max)
```

```{r}
# Time til each instar
data$tth <- 0
data$tt3 <- data$day.3rd - data$day.hatch
data$tt4 <- data$day.4th - data$day.hatch
data$tt5 <- data$day.5th - data$day.hatch
data$ttw <- data$day.w - data$day.hatch
data$ttrem <- data$day.remove - data$day.hatch
data$ttmax <- data$day.max - data$day.hatch

# Mass at each instar -> natural log of mass

data$lnh <- log(data$mass.hatch)
data$ln3 <- log(data$mass.3rd)
data$ln4 <- log(data$mass.4th)
data$ln5 <- log(data$mass.5th)
data$lnw <- log(data$mass.w)
data$lnrem <- log(data$mass.remove)
data$lnmax <- log(data$mass.max)

```

```{r}
masslong <- data %>% gather(instar, mass, mass.3rd, mass.4th, mass.5th, mass.max)
masslong$instar <- gsub("mass.", "", masslong$instar)
masslong$instar <- gsub("rd", "", masslong$instar)
masslong$instar <- gsub("th", "", masslong$instar)

agelong <- data %>% gather(instar, age, tth, tt3, tt4, tt5, ttmax)
agelong$instar <- gsub("tt", "", agelong$instar)

masslong <- masslong %>% select(ID, treatment, food, instar, mass)
agelong <- agelong %>% select(ID, treatment, food, instar, age)

datalong <- merge(masslong, agelong, by = c("ID", "treatment", "food", "instar"))


```



```{r}
lnmasslong <- data %>% gather(instar, mass, lnh, ln3, ln4, ln5, lnw, lnrem, lnmax)
lnmasslong$instar <- gsub("ln", "", lnmasslong$instar)

lnmasslong <- lnmasslong %>% select(ID, treatment, instar, mass)

lndatalong <- merge(lnmasslong, agelong, by=c("ID", "treatment", "instar"))
```

```{r}
devplot <- ggplot(datalong, aes(x = age, y = mass, group = ID, color = treatment, shape = food)) + 
  theme_bw() + 
  geom_point() +
  scale_shape_manual(values = c(1, 19)) + 
  geom_line(aes(linetype = food), alpha = 0.5) + 
  scale_linetype_manual(values = c("dotdash", "solid")) + 
  scale_color_viridis_d() + 
  labs(x = "Developmental age (days)", y = "Mass gained (mg)", shape = "Hostplant", linetype = "Hostplant", 
       color = "Treatment group")

devplot
```



```{r}
lndevplot <- ggplot(lndatalong, aes(x = age, y = mass, group = ID, color = treatment)) + 
  geom_point() +
  geom_line(alpha = 0.5) + 
  scale_color_viridis_d() + 
  labs(x = "Developmental age (days)", y = "Natural log of mass gained")

lndevplot
  
```


